\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-06 paper/paper.tex
edits in morning with eric.

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\subsection{Censoring and Truncation}
A common feature of lifetime data is right-censoring. In the analysis of reliability field data, it is rare all units are observed until failure. If a unit has not yet failed when the data are analyzed it is considered right-censored.  In other words, right-censoring puts a lower bound on the failure time.

@@

Probability plotting is a simple method to assess the adequacy of (log)location-scale families of probability models to the data.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with pointwise confidence bands provides a visual check for distributional goodness of fit.  We applied this method using the Kaplan-Meier nonparametric estimate of the empirical cdf.  With left truncation, however, the standard Kaplan-Meier estimator is biased, so we used an adjusted version due to\citet[Chapter 11, ]{meeker} (see Appendix for a detailed description).

@@

\section{Analysis of the Backblaze hard drive data}
\label{sec:Data analysis}
\subsection{Modeling}
We considered four models, all based on (\ref{eq:hier-model}), which are identified by which model parameters are held constant across drive-models. These are (from most to least restrictive):

@@

\subsubsection{Prior Distributions}
\label{sec:Prior Distributions}
To complete the full probability model, we need to select prior distributions for the parameters governing the hierarchical model. We select proper prior distributions to ensure a proper posterior distributions.

@@

\subsection{Results}
\subsubsection{Model Assessment}
\label{model-assessment}
Having chosen Model 4 as the best of the candidate models, we would like to assess whether our model provides an adequate description of the observed data. One way to do this is to draw replicate data sets from the posterior predictive distribution. This is a general approach recommended by \cite{gelman1996postpred} for models where no classical goodness-of-fit test is available. In the hierarchical setting, there can be different formulations of the predictive distribution. In the present context, one could predict the lifetime of a new unit of a previously observed drive-model or a new drive-model. We choose to focus on the first of these.  There are many possible approaches to the posterior predictive check. For this problem, we chose to consider the posterior predictive distribution of the Kaplan-Meier estimate for each drive-model $g$.

@@

\subsubsection{Drive-model Comparisons}
\label{subsubsec:Drive-model Comparisons}
We consider the problem of ranking drive-models. From a
business perspective, it is clear
that we should prefer the drive-models which will provide more years
of service. For ease of exposition, we will assume that the purchase
price of a hard-drive is the same across drive-models.

@@

We can also use the posterior draws to compute quantiles of interest, which in reliability applications is typically more informative than a measure of central tendency.  The top panel of Figure 9 shows $t_{0.10}$ (i.e., the amount of time it takes for 10\% of hard drives to fail), for all drive-models.  In this application 50\% CIs are more meaningful as there is lots of uncertainty in some of the parameters: especially for those with few drives in operation.  The best six drive-models ranked by MTTF are also the drive-models with the largest $t_{0.10}$.  Another interesting feature to compare is $\pi$, the proportion defective.  The bottom panel of Figure 10 shows the posterior credible intervals of $\pi$ for each drive-model.  The plot is again sorted according to $t_{0.10}$ so it can be compared to the plot above.  While for many of the drive-models the ordinal ranking is the same as on the top, there are some drive-model comparisons, for example 23 and 18, that differ in ranking if compared using $t_{0.10}$ or $\pi$.  Depending on a user's application or the hard drive warranty length, using the $\pi$'s as a comparison tool may be a relevant parameter of interest.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{dm-eval}
  \caption{Left: Summary of the posterior predictive distributions for $e^{-0.4 t_{g,new}}$ the depreciated value at failure (VAF) for a new unit for each Drive-model.
  Right: A comparison of the predictive distribution of TTF (top) and VAF (bottom) based on 40\% for best 11 drive-models, shows that rankings produced by the two measures are not equivalent.}
  \label{fig5}
\end{figure}

@@

First, we assume the failures occurring from various causes can be approximately assigned to two phases of product life.  In practice, there might be additional phases, clearly supported by the data, making the GLFP model too rigid. This rigidity is illustrated by the right tail of the estimated distribution in figure \ref{fig1}.

@@

While not presented here, another potential application is forecasting the number of future failures over a fixed period of time for a current population of drives. \citet{hmm} proposed a method, based on a Poisson binomial distribution. It would be straightforward to adapt their approach to work with our method. For details and examples see \citet[Sect.~6]{hmm} and \citet{xu2015assessing}.

@@

\item[Stan Code] Stan code for Model 4 (model4.pdf)

\item[Complete set of model comparison and model assessment plots] Posterior median of proportion failing as a function of time under Models 1-4 and posterior predictive graphical checks for all drive-models. (allplots.pdf)
\item[Backblaze hard-drive data] Lifetime data for all 44 drive-models used in our analysis. (backblaze\_hd\_data.csv)

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption, url}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\subsection{Censoring and truncation}
A common feature of lifetime data is right-censoring. In the analysis of reliability field data, it is rare all units are observed until failure. If a unit has not yet failed when the data are analyzed it is considered right-censored.  In other words, right-censoring puts a lower bound on the failure time.

@@

Probability plotting is a simple method to assess the adequacy of (log)location-scale families of probability models to the data.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with pointwise confidence bands provides a visual check for distributional goodness of fit.  We applied this method using the Kaplan-Meier nonparametric estimate of the empirical cdf.  With left truncation, however, the standard Kaplan-Meier estimator is biased, so we used an adjusted version due to \citet[Chapter 11]{meeker} (see Appendix for a detailed description).

@@

\section{Analysis of the Backblaze hard drive data}
\label{sec:Data analysis}
\subsection{Modeling}
\subsubsection{Hierarchical models}
We considered four models, all based on (\ref{eq:hier-model}), which are identified by which model parameters are held constant across drive-models. These are (from most to least restrictive):

@@

\subsubsection{Prior distributions}
\label{sec:Prior distributions}
To complete the full probability model, we need to select prior distributions for the parameters governing the hierarchical model. We select proper prior distributions to ensure a proper posterior distributions.

@@

\subsection{Results}
\subsubsection{Model assessment}
\label{model-assessment}
Having chosen Model 4 as the best of the candidate models, we would like to assess whether our model provides an adequate description of the observed data. One way to do this is to draw replicate data sets from the posterior predictive distribution. This is a general approach recommended by \cite{gelman1996postpred} for models where no classical goodness-of-fit test is available. In the hierarchical setting, there can be different formulations of the predictive distribution. In the present context, one could predict the lifetime of a new unit of a previously observed drive-model or a new drive-model. We choose to focus on the first of these.  There are many possible approaches to the posterior predictive check. For this problem, we chose to consider the posterior predictive distribution of the Kaplan-Meier estimate for each drive-model $g$.

@@

\subsubsection{Drive-model comparisons}
\label{subsubsec:Drive-model comparisons}
We consider the problem of ranking drive-models. From a
business perspective, it is clear
that we should prefer the drive-models which will provide more years
of service. For ease of exposition, we will assume that the purchase
price of a hard-drive is the same across drive-models.

@@

We can also use the posterior draws to compute quantiles of interest, which in reliability applications is typically more informative than a measure of central tendency.  The top panel of Figure 9 shows $t_{0.10}$ (i.e., the amount of time it takes for 10\% of hard drives to fail), for all drive-models.  In this application 50\% CIs are more meaningful as there is lots of uncertainty in some of the parameters: especially for those with few drives in operation.  The top seven drive-models ranked by MTTF are also the drive-models with the largest $t_{0.10}$.  Another interesting feature to compare is $\pi$, the proportion defective.  The bottom panel of Figure 9 shows the posterior credible intervals of $\pi$ for each drive-model.  The plot is again sorted according to $t_{0.10}$ so it can be compared to the plot above.  While for many of the drive-models the ordinal ranking is the same as on the top, there are some drive-model comparisons, for example 23 and 18, that differ in ranking if compared using $t_{0.10}$ or $\pi$.  Depending on a user's application or the hard drive warranty length, using the $\pi$'s as a comparison tool may be a relevant parameter of interest.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{dm-eval}
  \caption{Left: 90\% CI of the posterior predictive distributions for $e^{-0.4 t_{g,new}}$ the depreciated value at failure (VAF) for a new unit for each drive-model.
  Right: A comparison (90\% CI) of the predictive distribution of TTF (top) and VAF (bottom) based on 40\% for best 11 drive-models, shows that rankings produced by the two measures are not equivalent.}
  \label{fig5}
\end{figure}

@@

First, we assume the failures occurring from various causes can be approximately assigned to two phases of product life.  In practice, there might be additional phases, clearly supported by the data, making the GLFP model too rigid. This rigidity is illustrated by the right tail of the estimated distribution in Figure \ref{fig1}.

@@

While not presented here, another potential application is forecasting the number of future failures over a fixed period of time for a current population of drives. \citet{hmm} proposed a method, based on the Poisson-binomial distribution. It would be straightforward to adapt their approach to work with our method. For details and examples see \citet[Sect.~6]{hmm} and \citet{xu2015assessing}.

@@

\item[Stan Code and Plots] Stan code for Model 4 as well as the complete set of plots for Figures 5 and 6 (supplementary.pdf)

\item[Backblaze hard-drive data] Lifetime data set for all 44 drive-models used in our analysis. (backblaze\_hd\_data.csv)
